% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\usepackage{enumitem}
\hypersetup{
  colorlinks,%
  citecolor=black,%
  filecolor=black,%
  linkcolor=black,%
  urlcolor=black
  %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
	#1 & #2 \\
    {#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}}

\newcommand{\ressubsubheading}[2]{
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
	\textit{#1} & \textit{#2} \\
  \end{tabular*}\vspace{-7pt}}

\newcommand{\ressubsubheadingni}[2]{
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
	#1 & #2 \\
  \end{tabular*}\vspace{-7pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Mingdong Wang}} &{(+86) 18056890252}\\
	& \href{mailto:kevinwangthu@gmail.com}{kevinwangthu@gmail.com}\\
    & Room 324, Building No.28, Tsinghua University, Beijing, China
  \end{tabular*}
  \\
  \vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
\begin{itemize}
\item
  \ressubheading{\href{http://www.tsinghua.edu.cn}{\textbf{Tsinghua University}}}{Beijing, China}{\textit{B.S. in Math and Physics, Minor in Computer Technology}}{Aug. 2012 -- July 2016(expected)}
	            {
%                  \ressubsubheading{Minor in Computer Technology}{}
                  \footnotesize
				  \begin{itemize}
                    \resitem{\textbf{GPA: Overall: 89.8/100\quad Major: 90.0/100}}
                    \resitem{Related Courses: Advanced Calculus, Advanced Algebra, Stochastic Mathematical Methods, Experiments in Math, Discrete Math, Introduction to AI, Java and OOP, C++ Programming for Linux}
				  \end{itemize}
				}
		      \item
			    \ressubheading{\href{http://www.ust.hk}{\textbf{Hong Kong University of Science and Technology}}}{Clear Water Bay, Hong Kong}{\textit{Exchange Student, School of Science}}{Aug. 2014 - Dec. 2014}
				              { \footnotesize
				                \begin{itemize}
				                  \resitem{\textbf{GPA: 4.071/4.3}, Dean's List}
                                  \resitem{Related Courses: Honor OOP and Data Structure, Honor Design and Analysis of Algorithms}
				                \end{itemize}
				              }

\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
\begin{itemize}
\item
  \ressubsubheadingni{\textbf{Research Assistant}, \textit{Advised by Prof. Minlie Huang}}{CS Dept., THU}{\vspace{5pt}
    \ressubsubheading{\textbf{Neural Document Summarization}}{Jan. 2016 - Present}{
      \footnotesize
      \begin{itemize}
        \resitem{Proposed a neural network model inspired by machine translation}
        \resitem{Utilized multi-layer RNN/LSTM and attention model}
        \resitem{Python, Theano}
      \end{itemize}
      }

    \ressubsubheading{\textbf{Domain Adaptation for Sentiment Classification}}{Sept. 2015 - Dec. 2015}{
      \footnotesize
      \begin{itemize}
        \resitem{Designed a Bi-Shift Autoencoder for classifiers' adaptation of product reviews from different domains}
        \resitem{Combined autoencoder and sparse linear regression to extract higher level features from raw text}
        \resitem{Implemented a Co-Training algorithm to learn a bilingual sentiment classifier}
        \resitem{Languages: Matlab, Python}
      \end{itemize}
    }
    \ressubsubheading{\textbf{Knowledge Graph Embedding by Flexible Translation}}{\textit{Mar. 2015 - Sept. 2015}}{
      \footnotesize
      \begin{itemize}
        \resitem{Proposed a flexible translation principle to better embed multi-relational knowledge graph into $\mathbb{R}^k$}
        \resitem{Utilized SGD to minimize a margin-based loss function, conducted extensive experiments}
        \resitem{Improved existing models with our principle and achieved state-of-art results}
        \resitem{Language: C++}
      \end{itemize}
    }
    }


\end{itemize}  % End Experience list

\resheading{Publication}
\begin{itemize}
  \resitem{Jun Feng, Minlie Huang, \textbf{Mingdong Wang}, Mantong Zhou, Yu Hao, and Xiaoyan Zhu, Knowledge Graph Embedding by Flexible Translation. Submitted to KR-16.}
\end{itemize}

\resheading{Projects}
\begin{description}
\item[microScheme] {A simplified but Turing complete Scheme interpreter with many syntax sugars like \emph{let}. Implemented many library functions like \emph{for-each}, \emph{assoc} and \emph{quicksort}. Implemented in C++ and documented by Doxygen.}
\item[PhyDesktop] {A GUI software that manages class activities. Functions include login, user calendar, creating and sending notifications, supported by a database on server. Implemented in Java.}
\end{description}

\resheading{Awards and Honors}
\begin{itemize}
\item\ressubsubheadingni{First Prize in 30-th College Physics Competition in Part of China}{2013}
\item\ressubsubheadingni{Social Work and Practice Scholarship of Tsinghua University}{2013}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
\begin{description}
\item[Languages \& Tools] {C/C++, Python, Theano, Matlab, Haskell, Linux, \LaTeX, Emacs}
%  \item[]
\end{description} % End Skills list


\begin{comment}
  \resheading{Standardized Tests}
  \begin{description}
  \item[TOEFL] {R: 30, L: 29, S: 23, W: 25, Total:107}
  \item[GRE] {V: 156, Q: 170, AW: 3.5}
  \end{description}
\end{comment}

\end{document}
